%-------------------------
% ATS-Friendly Resume in LaTeX
% Author: Kevin George Leo
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\input{glyphtounicode}

% Font
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

% Page style
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\usepackage[top=0.6in, bottom=0.6in, left=0.6in, right=0.6in]{geometry}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% ATS-friendly section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% PDF metadata for ATS
\hypersetup{
  pdftitle={Kevin George Leo - Resume},
  pdfauthor={Kevin George Leo},
  pdfsubject={Computer Science, Security, Web Development},
  pdfkeywords={Security, Web Security, Python, JavaScript, Node.js, Deno, Bun, Playwright, SQL, Linux}
}

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Kevin George Leo} \\ \vspace{4pt}
    \small +49 15510 526441 $|$
    \href{mailto:kevgeoleo1999@gmail.com}{\underline{kevgeoleo1999@gmail.com}} $|$
    \href{https://www.linkedin.com/in/kevin-george-leo-481b34249/}{\underline{Linkedin}} $|$
    \href{https://github.com/kevgeoleo}{\underline{github.com/kevgeoleo}} $|$
    Germany
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\small{
Security researcher and software engineer with 2+ years of industry experience and active research in web security, JavaScript runtime differential testing, and vulnerability disclosure. Skilled in Python, JavaScript, and automated testing pipelines. Experienced in responsible disclosure with 6 CVEs and 1 GitHub Security Advisory. Pursuing MSc Computer Science at Saarland University with a GPA of 1.5.
}

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Hilfswissenschaftler (Research Assistant)}{May 2024 -- Present}
      {CISPA Helmholtz Center for Information Security}{Saarbrücken, Germany}
      \resumeItemListStart
        \resumeItem{Conducted security research in the web domain using differential testing of JavaScript runtimes including Node.js, Deno, and Bun.}
        \resumeItem{Designed and implemented an automated testing pipeline in Python to execute test suites across multiple runtimes and post-process results for vulnerability detection.}
        \resumeItem{Reported and responsibly disclosed security bugs to runtime maintainers via GitHub Issues.}
        \resumeItem{Built a proof-of-concept UI deception attack leveraging Progressive Web Apps (PWAs) on V8-based browsers using HTML, CSS, and JavaScript to demonstrate real-world impact.}
        \resumeItem{Developed an automated Playwright-based framework to simulate user authentication flows in 2FA-based environments.}
      \resumeItemListEnd

    \resumeSubheading
      {Programmer Analyst}{Aug 2021 -- Sep 2023}
      {Cognizant Technology Solutions}{Kochi, India}
      \resumeItemListStart
        \resumeItem{Worked as a Production Support Engineer on a health insurance data warehousing project, supporting business-critical ETL pipelines.}
        \resumeItem{Monitored, triaged, and resolved production incidents following structured incident response workflows, using ServiceNow, Linux shell scripting, IBM DataStage, and SQL.}
        \resumeItem{Conducted Root Cause Analysis (RCA) as part of post-incident review, identifying systemic failures and preventing recurrence.}
        \resumeItem{Implemented remediation and preventive controls to improve pipeline reliability and reduce incident volume.}
        \resumeItem{Prepared incident reports and SLA documentation; communicated incident status, risk assessments, and resolutions to technical and business stakeholders.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart

    \resumeSubheading
      {University of Saarland}{Oct 2023 -- Present}
      {MSc Computer Science}{Saarbrücken, Germany}
      \resumeItemListStart
        \resumeItem{GPA: 1.5 (German scale)}
        \resumeItem{Relevant Courses: Security, Web Security, Human Computer Interaction, Data Networks, Software Engineering}
        \resumeItem{Completed CTF (Capture the Flag) challenges in Web Security coursework, covering topics such as [XSS / SQLi / CSRF / UI Deception]}
      \resumeItemListEnd

    \resumeSubheading
      {Rajagiri School of Engineering and Technology}{Jul 2017 -- Jun 2021}
      {Bachelor of Technology, Computer Science and Engineering}{India}
      \resumeItemListStart
        \resumeItem{GPA: 9.29 / 10}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS AND THESIS-----------
\section{Projects and Thesis}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Master Thesis:} Study on Cross-Runtime Bug Transference and Robustness of Fixes}{2026}
          \resumeItemListStart
            \resumeItem{Developed an automated pipeline using LLMs to generate proof-of-concept (PoC) exploits from GitHub issue reports.}
            \resumeItem{Executed PoCs across multiple JavaScript runtimes to detect behavioral divergences and recurring bugs.}
            \resumeItem{Evaluated the impact of runtimes on vulnerable npm packages and their execution behavior.}
            \resumeItem{Designed AST-based mutation techniques to test the robustness of vulnerability patches.}
            \resumeItem{Discovered 141 bugs, of which 127 are confirmed (110 previously unreported) across major JavaScript runtimes.}
            \resumeItem{Uncovered 57 weak security fixes in npm packages; responsible disclosure resulted in 6 CVEs (CVE-2026-25521, CVE-2026-25047, CVE-2026-26021, CVE-2026-27212, CVE-2026-28491, CVE-2026-33864) and 1 GitHub Security Advisory (GHSA-gcrg-hrj9-ggqg).}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Chemical Structure Drawing Tool}}{Jan 2020 -- Dec 2021}
          \resumeItemListStart
            \resumeItem{Developed a web-based exam platform for high school students with an integrated chemical structure drawing tool.}
            \resumeItem{Built using HTML, CSS, JavaScript, PHP, and SQL; developed solution for representing and evaluating chemical structure data using Python and SQL.}
            \resumeItem{Managed all stages of the Software Development Life Cycle (SDLC); documented project using LaTeX.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:} Python, JavaScript, PHP, SQL, C, C++, R, Unix Shell \\
     \textbf{Web Technologies:} HTML, CSS, Node.js, Deno, Bun, Progressive Web Apps (PWA) \\
     \textbf{Testing \& Automation:} Playwright, Differential Testing, AST Mutation (Acorn, Estraverse) \\
     \textbf{Security Tools:} Autopsy, Hashcat \\
     \textbf{Developer Tools:} Git, Linux, Figma, LaTeX, OpenAI API, IBM DataStage, ServiceNow \\
     \textbf{Databases:} SQL \\
     \textbf{Other:} MS Office, LLM-based automation pipelines
    }}
 \end{itemize}

%-----------NON-TECHNICAL SKILLS-----------
\section{Non-Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Analytical Thinking, Problem Solving, Written and Verbal Communication, Team Collaboration, Self-Initiative
    }}
 \end{itemize}

%-----------LANGUAGES-----------
\section{Languages}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{English:} C1 (Professional Working Proficiency) \quad
     \textbf{German:} A2 (Elementary)
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
